RDF Validation Requirements - Evaluation and Logical Underpinning

### 2014-12-26 paper/RDF validation requirements/RDF validation requirements.tex
research questions and contributions

\section{Equivalent Properties}

\begin{itemize}
	\item An equivalent object properties axiom EquivalentObjectProperties( OPE1 ... OPEn ) states that all of the object property expressions OPEi, 1 $\leq$ i $\leq$ n, are semantically equivalent to each other. This axiom allows one to use each OPEi as a synonym for each OPEj — that is, in any expression in the ontology containing such an axiom, OPEi can be replaced with OPEj without affecting the meaning of the ontology. The axiom EquivalentObjectProperties( OPE1 OPE2 ) is equivalent to the following two axioms SubObjectPropertyOf( OPE1 OPE2 ) and SubObjectPropertyOf( OPE2 OPE1 ).
	\item An equivalent data properties axiom EquivalentDataProperties( DPE1 ... DPEn ) states that all the data property expressions DPEi, 1 $\leq$ i $\leq$ n, are semantically equivalent to each other. This axiom allows one to use each DPEi as a synonym for each DPEj — that is, in any expression in the ontology containing such an axiom, DPEi can be replaced with DPEj without affecting the meaning of the ontology. The axiom EquivalentDataProperties( DPE1 DPE2 ) can be seen as a syntactic shortcut for the following axiom SubDataPropertyOf( DPE1 DPE2 ) and SubDataPropertyOf( DPE2 DPE1 ).

@@

\begin{DL}
:hasBrother $\sqsubseteq$ :hasMaleSibling $\sqcap$ :hasMaleSibling $\sqsubseteq$ :hasBrother \\
equivalent to: $hasBrother = hasMaleSibling$
\end{DL}

@@

\begin{itemize}
	\item Meg is not a son of Peter.
\end{itemize}

\begin{DL}
$hasSon(\textbf{Peter},\textbf{Meg})$\\
(negation of such an assertion is not necessary / meaningless!)
\end{DL}

@@

\begin{itemize}
	\item Meg is seventeen years old. 
\end{itemize}

\begin{DL}
$hasAge ( \textbf{Meg} ,\textbf{ "17"}\hat{\ } \hat{\ } xsd:integer ) $\\
\end{DL}

@@

\begin{itemize}
	\item An object property functionality axiom FunctionalObjectProperty( OPE ) states that the object property expression OPE is functional — that is, for each individual x, there can be at most one distinct individual y such that x is connected by OPE to y. Each such axiom can be seen as a syntactic shortcut for the following axiom: SubClassOf( owl:Thing ObjectMaxCardinality( 1 OPE ) ).
\end{itemize}

@@

\begin{itemize}
	\item Each object can have at most one father. 
\end{itemize}

@@

@@

\begin{itemize}
	\item An object property inverse functionality axiom InverseFunctionalObjectProperty( OPE ) states that the object property expression OPE is inverse-functional — that is, for each individual x, there can be at most one individual y such that y is connected by OPE with x. Each such axiom can be seen as a syntactic shortcut for the following axiom: SubClassOf( owl:Thing ObjectMaxCardinality( 1 ObjectInverseOf( OPE ) ) ).
\end{itemize}

@@

>>>>

\section{Equivalent Properties}
An equivalent object properties axiom EquivalentObjectProperties( OPE1 ... OPEn ) states that all of the object property expressions OPEi, 1 $\leq$ i $\leq$ n, are semantically equivalent to each other. This axiom allows one to use each OPEi as a synonym for each OPEj — that is, in any expression in the ontology containing such an axiom, OPEi can be replaced with OPEj without affecting the meaning of the ontology. The axiom EquivalentObjectProperties( OPE1 OPE2 ) is equivalent to the following two axioms SubObjectPropertyOf( OPE1 OPE2 ) and SubObjectPropertyOf( OPE2 OPE1 ).

An equivalent data properties axiom EquivalentDataProperties( DPE1 ... DPEn ) states that all the data property expressions DPEi, 1 $\leq$ i $\leq$ n, are semantically equivalent to each other. This axiom allows one to use each DPEi as a synonym for each DPEj — that is, in any expression in the ontology containing such an axiom, DPEi can be replaced with DPEj without affecting the meaning of the ontology. The axiom EquivalentDataProperties( DPE1 DPE2 ) can be seen as a syntactic shortcut for the following axiom SubDataPropertyOf( DPE1 DPE2 ) and SubDataPropertyOf( DPE2 DPE1 ).

@@

\begin{DL}
:hasBrother $\sqsubseteq$ :hasMaleSibling $\sqcap$ :hasMaleSibling $\sqsubseteq$ :hasBrother \\
\end{DL}

\begin{gcotable}
property & $\top$ & hasBrother & hasMaleSibling & - & $\sqsubseteq$ \\
property & $\top$ & hasMaleSibling & has Brother & - & $\sqsubseteq$ \\
\end{gcotable}

\begin{DL}
$hasBrother \equiv hasMaleSibling$
\end{DL}

@@

Meg is not a son of Peter.

\begin{DL}
$hasSon(Peter,Meg)$\\
\end{DL}

The negation of such an assertion is not necessary, as it's meaningless!

\begin{gcotable}
class & \{Peter\} & hasSon & - & \{Meg\} & $\neq$ & - \\
\end{gcotable}

@@

Meg is seventeen years old.

\begin{DL}
$hasAge ( Meg ,"17"\hat{\ } \hat{\ } xsd:integer ) $\\
\end{DL}

\begin{gcotable}
class & \{Meg\} & hasAge & - & - & = & "17"$\hat{\ } \hat{\ }$ xsd:integer \\
\end{gcotable}

@@

An object property functionality axiom FunctionalObjectProperty( OPE ) states that the object property expression OPE is functional — that is, for each individual x, there can be at most one distinct individual y such that x is connected by OPE to y. Each such axiom can be seen as a syntactic shortcut for the following axiom: SubClassOf( owl:Thing ObjectMaxCardinality( 1 OPE ) ).

@@

Each object can have at most one father.

@@

\begin{gcotable}
property & $\top$ & hasFather & - & - & functional & - \\
\end{gcotable}

@@

An object property inverse functionality axiom InverseFunctionalObjectProperty( OPE ) states that the object property expression OPE is inverse-functional — that is, for each individual x, there can be at most one individual y such that y is connected by OPE with x. Each such axiom can be seen as a syntactic shortcut for the following axiom: SubClassOf( owl:Thing ObjectMaxCardinality( 1 ObjectInverseOf( OPE ) ) ).

@@

\begin{gcotable}
property & $\top$ & hasFather$^{-}$ & hasFather & - & inverse & - \\
property & $\top$ & hasFather$^{-}$ & - & - & functional & - \\
\end{gcotable}
